### 2025-09-13 about/vita.tex
Started 242 tutorials

\leftright{\bf Co-Editor}{\bf December 2023 -- present}
\leftright{\sl Ahoy Literary Magazine}{\sl Montr\'eal, QC, Canada}
\smallskip
Founding co-editor of a semiannual print magazine that publishes poetry, prose, and art.
In charge of English short fiction submissions and the overall typesetting. Share duties with the other
co-editors related to marketing, emails, and sales.
\medbreak

@@

\starleftright{\bf Teaching assistant}{\bf September 2021 -- April 2024}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant in the following courses. Duties include giving tutorials, holding office hours, and
grading assignments and exams.
\begingroup\parindent=10pt
\smallskip
\thing Winter 2024, Fall 2023: MATH 240 Discrete Structures
\smallskip
\thing Fall 2021: COMP 690 Probabilistic Analysis of Algorithms
\endgroup
\medbreak

@@

\starleftright{\bf Summer camp counsellor}{\bf June -- August 2014}
\leftright{\sl YoWoChAs Outdoor Education Centre}{\sl Fallis, AB, Canada}
\smallskip
Led children aged 4--15 through various activities (e.g. archery, canoeing, zipline) at a sleepaway camp.
\medbreak

>>>>

\leftright{\bf Editor-in-Chief}{\bf December 2023 -- present}
\leftright{\sl Ahoy Literary Magazine}{\sl Montr\'eal, QC, Canada}
\smallskip
Founding member and one of two editors-in-chief of
a semiannual print magazine that publishes poetry, prose, and art.
In charge of English short fiction submissions and the overall typesetting. Share duties with the other
editors related to emails, sales, and magazine launches.
\medbreak

\starleftright{\bf Teaching assistant}{\bf September 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant in the following courses. Duties include giving tutorials, holding office hours, and
grading assignments and exams.
\begingroup\parindent=10pt
\smallskip
\thing Fall 2025: MATH 242 Analysis 1
\smallskip
\thing Winter 2024, Fall 2023: MATH 240 Discrete Structures
\smallskip
\thing Fall 2021: COMP 690 Probabilistic Analysis of Algorithms
\endgroup
\medbreak

@@

@@

\starleftright{\bf Summer camp counsellor}{\bf June -- August 2014}
\leftright{\sl YoWoChAs Outdoor Education Centre}{\sl Fallis, AB, Canada}
\smallskip
Led children aged 4--15 through various activities (e.g., archery, canoeing, zipline) at a sleepaway camp.
\medbreak

### 2025-09-13 misc/expo/idempotent.tex
Started 242 tutorials

\def\eps{\epsilon}
\def\FF{\hbox{\bf F}}
\def\bar#1{\overline{#1}}
\def\hat#1{\widehat{#1}}
\def\norm#1{|\!|#1|\!|}
\def\bignorm#1{\big|\!\big|#1\big|\!\big|}
\def\Norm#1{\Big|\!\Big|#1\Big|\!\Big|}
\def\normm#1{\bigg|\!\bigg|#1\bigg|\!\bigg|}
\def\argmax{\limitop{\rm arg$\,$max}}
\def\dTV{d_{\rm TV}}

@@

@@

{\sc A topological abelian group} is a Hausdorff space that is also an abelian group, such that
the map from $G\times G$ to $G$ sending $(x,y) \mapsto x-y$ is continuous (where the topology
on $G\times G$ is the product topology).
If, in addition, every point in $G$ is contained in some compact neighbourhood of $G$, then
$G$ is said to be a {\it locally compact abelian} group.

@@

\proof Let $x,y\in \bar H$ and suppose, for a contradiction, that $xy\notin \bar H$. :

A topological space is called {\it discrete} if for every point $p$ in it, the singleton set $\{p\}$
is open.

Let $G$ be a locally compact abelian group.
The set of all measures $\mu$ on $G$ forms a topological semigroup under the convolution operation
$$\mu * \nu = \int_G

>>>>

\def\eps{\epsilon}
\def\FF{\hbox{\bf F}}
\def\bar#1{\overline{#1}}
\def\hat#1{\widehat{#1}}
\def\norm#1{|\!|#1|\!|}
\def\bignorm#1{\big|\!\big|#1\big|\!\big|}
\def\Norm#1{\Big|\!\Big|#1\Big|\!\Big|}
\def\normm#1{\bigg|\!\bigg|#1\bigg|\!\bigg|}
\def\argmax{\limitop{\rm arg$\,$max}}
\def\dTV{d_{\rm TV}}
\def\d{\;d}

@@

\advsect Topological preliminaries

A {\it topology} on a set $S$ is a collection of subsets of $S$ that contains the empty set and
is closed under the formation of unions and finite intersections. If $S$ has a topology defined on it,
then $S$ is said to be a {\it topological space}, and the members of its topology are called
{\it open sets}. The complements of open sets are called {\it closed sets}.

\edef\propopencriterion{\the\thmcount}
\proclaim Proposition \advthm. A set $A$ is open if and only if for every $x\in A$, there is an open
set $U_x$ with $x\in U_x$ and $U_x\subseteq A$.

\proof If $A$ is open, then for any $x\in A$ we can simply take $U = A$. Conversely, if for every
point $x\in A$ there is some open $U_x\subseteq A$ with $x\in U_x$, then $A = \bigcup_{x\in A} U_x$,
so $A$ is open, being a union of open sets.\slug

The largest
open set contained in a set $A$ is the {\it interior} of $A$, and the smallest closed set containing
$A$ is its {\it closure}, denoted $\bar A$. If $A\bar A$ is the whole set $S$, then we say $A$ is
{\it dense} in $S$, and if some countable set is dense in $S$, then $S$ is a {\it separable} space.

A set $A$ is said to be a {\it neighbourhood} of a point $p$ if $p$ belongs to the interior of $A$.
The space $S$ is called {\it Hausdorff} if for all points $x,y\in S$ with $x\ne y$, there is some
open neighbourhood $U$ of $X$ and open neighbourhood $V$ of $y$ such that $U\cap V=\emptyset$.
A set $A$ is {\it compact} if every open cover of $A$ has a finite subcover. If every point of $S$
has some compact neighbourhood, then $S$ is called {\it locally compact}.

If the singleton set $\{p\}$ is open, then $p$ is called an {\it isolated point} of $S$, and if
$p$ is isolated for all points $p\in S$, then $S$ is a {\it discrete space}.

\medskip\boldlabel Limit points of nets.
A relation $\preceq$ on a set $I$ is a {\it preorder} if it is reflexive and transitive.
A set $I$ is said to be {\it directed} if there exists a preorder $\preceq$ on it such that
any two elements have an upper bound; that is,
for all $i,j\in I$, there exists $k\in I$ such that $i\preceq k$ and $j\preceq k$.

Let $I$ be a directed set and $S$ any set. A function $f:I\to S$ is called
a {\it net}. We usually index the elements of the net by elements of $I$; writing $x_i = f(i)$ for all
$i\in I$, the net $f$ can be expressed as $(x_i)_{i\in I}$. When $I = \NN$ under the usual ordering
$\le$, we recover the usual definition of a {\it sequence} of points in $S$.
We say that $(x_i)_{i\in I}$ is {\it eventually} in $A$ if there exists some $j\in I$ such that for all
$i \succeq j$, $x_i\in A$. A point $x\in S$ is called a {\it limit point} of $(x_i)_{i\in I}$ if
for every open neighbourhood $U$ of $x$, the net $(x_i)_{i\in I}$ is eventually in $U$. In this
case we write $x_i\to x$.

\proclaim Proposition \advthm. If $S$ is a Hausdorff space, then every net $(x_i)_{i\in I}$ valued
in $S$ has at most one limit point.

\proof Let $S$ be a topological space and suppose there is a net $(x_i)_{i\in I}$ with two distinct
limit points $x$ and $y$. Let $U$ be an open neighbourhood of $x$ and $V$ an open neighbourhood of $Y$.
By definition of limit point, there is some $i\in I$ such that $x_k \in U$ for all $k\succeq i$,
and similarly there is some $j\in I$ such that $x_i\in V$ for all $k\succeq j$. But since $I$
is a directed set, there must exist some $k\in I$ with $k\succeq i$ and $k\succeq j$, and we find
that $x_k\in U\cap V$. Since $U$ and $V$ were arbitrary, we conclude that $S$ is not Hausdorff.\slug

In light of the proposition, so long as the ambient space is Hausdorff it makes sense to write
$\lim_{i\in I} x_i = x$ whenever the limit point of $(x_i)_{i\in I}$ is $x$. We may also choose
to write $x_i \to x$.

We now introduce a common choice of directed set that features in some of the proofs below.

\edef\propnbhdnet{\the\thmcount}
\proclaim Proposition \advthm.
Let $x$ be a point in a topological space $S$ and let $N(x)$ be the set of all open neighbourhoods
of $x$. Define an order on $N(x)$ by declaring $U\preceq V$ if and only if $U\supset V$. Then the order
$\preceq$ is directed, and $x$ is a limit point of any
net $(x_U)_{U\in N(x)}$ satisfying $x_U\in U$ for all $U\in N(x)$.

\proof The set $N(x)$ is clearly directed, since for every $U,V\in N(x)$,
$U \supset U\cap V$ and $V\supset U\cap V$. Now let $(x_U)_{U\in N(x)}$ be any net with
$x_U\in U$ for all $U\in N(x)$. Pick any open set $V$ containing $x$. This set $V$ is a member of
$N(x)$, and for any $U\in N(x)$ with $U\succeq V$, we must have $x_U\in U \subseteq V$.\slug

One can characterise closed sets in terms of limit points of nets.

\proclaim Proposition \advthm. A set $A$ is closed if and only if whenever a
net with $(x_i)_{i\in I}$ satisfying $x_i\in A$ for all $i\in I$ possesses a limit point $x$,
we must have $x\in A$.

\proof Suppose that $A$ is closed and let $(x_i)_{i\in I}$ be a net with limit point $x$
and $x_i\in A$ for all $i\in I$. For a contradiction, suppose that $x\notin A$. Then $x \in A^c$,
which is open. By the definition of limit point, there exists $j$ such that $x_i\in A^c$ for all
$j\succeq i$. This contradicts the assumption that $x$ is a limit point of $(x_i)_{i\in I}$.

Now we assume the second condition and prove that $A^c$ is open.
Let $N(x)$ be the set of all open neighbourhoods of $x$.
Towards a contradiction, assume
that there is some $x\in A^c$ such that for all $U\in N(x)$, we have $U\cap A \ne \emptyset$.
So for all $U\in N(x)$, we may pick $x_U\in U\cap A$, and the net $(x_U)_{U\in N(x)}$
has $x$ as its limit point, by Proposition~{\propnbhdnet}. But $x_U\in A$ for all $U\in N(x)$,
so by our assumption, we must have $x\in A$. This contradiction shows that
any $x\in A^c$ must have some open neighbourhood $U$ that is contained in $A^c$. Hence by
Proposition~{\propopencriterion}, $A$ is closed.\slug

@@

A topological abelian group is an abelian group $G$ endowed with the topology of a Hausdorff
space, such that
the map from $G\times G$ to $G$ sending $(x,y) \mapsto x-y$ is continuous. (The topology
on $G\times G$ is taken to be the product topology).
If, in addition, $G$ is also locally compact, then
$G$ is said to be a {\it locally compact abelian} group.

@@

\proof Let $x,y\in \bar H$ and let $Z$ be any neighbourhood of $x-y$. Since multiplication
is continuous (and by the definition of the product topology), there is an open neighbourhood
$X$ of $x$ and $Y$ of $y$ such that $X-Y\subseteq Z$. By the definition of closure,
there are points $a\in X\cap H$ and $b\in Y\cap H$. The point $a-b$ is in $H$ because $H$ is a subgroup,
and thus $a-b\in Z\cap H$.\slug

Let $G$ be a locally compact abelian group.
The set of all measures $\mu$ on $G$ forms a topological semigroup under the convolution operation
$$\mu * \nu(A)  = \int_G \chi_A(x+y) \d \mu(x) \d\nu(x),$$
where $\chi_A$ denotes the characteristic function of $A$.
